### 2014-09-15 paper.tex
Added more to the meta data section and formatted the marker table in latex.

Each trial directory contains a meta data file in the YML format. There are
three main headings: \verb+study+, \verb+subject+, and \verb+trial+.

The \verb+study+ section contains identififying informatio for the overall
study, an identification number, name, and description. This is the same for
all meta data files in the study.

@@

\todo[inline]{Add and example meta data file here with explanations of each
field.}

@@

\begin{table}
  \begin{tabular}{rlll}
    1 & LHEAD & Left head & Just above the ear, in the middle. \\
    2 & THEAD & Top head & On top of the head, in line with the LHEAD and RHEAD. \\
    3 & RHEAD & Right head & Just above the ear, in the middle. \\
    4 & FHEAD & Forehead & Between line LHEAD/RHEAD and THEAD a bit right from center. \\
    5 & C7 & C7 & On the 7th cervical vertebrae. \\
    6 & T10 & T10 & On the 10th thoracic vertbrae. \\
    7 & SACR & Sacrum bone & on the scacral bone. \\
    8 & NAVE & Navel & On the navel. \\
    9 & XYPH & Xiphoid process & Xiphoid process of the sternum. \\
    10 & STRN & Sternum & On the jugular notch of the sternum. \\
    11 & BBAC & Scapula & On the inferior angle fo the right scapular. \\
    12 & LSHO & Left shoulder & Left acromion. \\
    13 & LDELT & Left deltoid muscle & Apex of the deltoid muscle. \\
    14 & LLEE & Left lateral elbow & Left lateral epicondyle of the elbow. Upper one in the T-Pose. \\
    15 & LMEE & Left medial elbow & Left medial epicondyle of the elbow. Lower on in the T-Pose. \\
    16 & LFRM & Left forearm & On 2/3 on the line between the LLEE and LMW. \\
    17 & LMW & Left medial wrist & On styloid process radius, thumb side. \\
    18 & LLW & Left lateral wrist & On styloid process ulna, pinky side. \\
    19 & LFIN & Left fingers & Center of the hand. Caput metatarsal 3. \\
    20 & RSHO & Right shoulder & Right acromion. \\
    21 & RDELT & Right deltoid muscle & Apex of deltoid muscle. \\
    22 & RLEE & Right lateral elbow & Right lateral epicondyle of the elbow. Lower one in the T-pose. \\
    23 & RMEE & Right medial elbow & Right medial epicondyle of the elbow. Lower one in the T-pose. \\
    24 & RFRM & Right forearm & On 1/3 on the line between the RLEE and RMW. \\
    25 & RMW & Right medial wrist & On styloid process radius, thumb side. \\
    26 & RLW & Right lateral wrist & On styloid process ulna, pinky side. \\
    27 & RFIN & Right fingers & Center of the hand. Caput metatarsal 3. \\
    28 & LASIS & Pelvic bone left front & Left anterio superior iliac spine. \\
    29 & RASIS & Pelvic bone right front & Right anterior superior iliac spine. \\
    30 & LPSIS & Pelvic bone left back & Left posterior superio iliac spine. \\
    31 & RPSIS & Pelvic bone right back & Right posterior superior iliac spine. \\
    32 & LGTRO & Left greater trochanter of the femur & On the cetner of the left greater trochanter. \\
    33 & FLTHI & Left thigh & On 1/3 on the line between the LFTRO and LLEK. \\
    34 & LLEK & Left lateral epicondyle of the knee & On the lateral side of the joint axis. \\
    35 & LATI & Left anterior of the tibia & On 2/3 on the line between the LLEK and LLM. \\
    36 & LLM & Left lateral malleoulus of the ankle & The center of the heel at the same height as the toe. \\
    37 & LHEE & Left heel & Center of the heel at the same height as the toe. \\
    38 & LTOE & Left toe & Tip of big toe. \\
    39 & LMT5 & Left 5th metatarsal & Caput of the 5th metatarsal bone, on joint line midfoot/toes. \\
    40 & RGTRO & Right greater trochanter of the femur & On the cetner of the right greater trochanter. \\
    41 & FRTHI & Right thigh & On 2/3 on the line between the RFTRO and RLEK. \\
    42 & RLEK & Right lateral epicondyle of the knee & On the lateral side of the joint axis. \\
    43 & RATI & Right anterior of the tibia & On 1/3 on the line between the RLEK and RLM. \\
    44 & RLM & Right lateral malleoulus of the ankle & The center of the heel at the same height as the toe. \\
    45 & RHEE & Right heel & Center of the heel at the same height as the toe. \\
    46 & RTOE & Right toe & Tip of big toe. \\
    47 & RMT5 & Right 5th metatarsal & Caput of the 5th metatarsal bone, on joint line midfoot/toes. \\
  \end{tabular}
  \label{tab:marker-labels}
\end{table}

>>>>

Each trial directory contains a meta data file in the YAML format. There are
three main headings: \verb+study+, \verb+subject+, and \verb+trial+.

The \verb+study+ section contains identififying information for the overall
study, an identification number, name, and description. This is the same for
all meta data files in the study.

@@

An example meta data file is shown in Figure \ref{fig:example-meta-data} and
the following gives and explanation of the contents.

\begin{figure}
  \small
  \begin{verbatim}
    study:
            id: 1
            name: Gait Control Identification
            description: Perturb the subject during walking and running.
    subject:
            id: 0
    trial:
            id: 58
            subject-id: 0
            datetime: 2014-03-28
            notes: >
                    This is an unloaded trial (no subject) 10 minute protocol that
                    perturbs the subject longitudinally. The treadmill reference
                    markers were not in place. We have the four custom made metal
                    feet placed under the four corners of the treadmill to prevent
                    pitch and sway movements. In addition, we also have the front
                    left and rear right feet that were installed by Motek. We also
                    have +/-3g analog accelerometers (ADXL330) affixed to the four
                    corners of the main frame of the treadmill and wired into the
                    NI box. The right handrail is removed.
            nominal-speed: 0.8
            nominal-speed-units: meters per second
            stationary-platform: True
            pitch: False
            sway: False
            hardware-settings:
                    high-performance: True
            analog-channel-map:
                    Channel1.Anlg: F1Y1
                    Channel2.Anlg: F1Y2
                    Channel3.Anlg: F1Y3
                    Channel4.Anlg: F1X1
                    Channel5.Anlg: F1X2
                    Channel6.Anlg: F1Z1
                    Channel7.Anlg: F2Y1
                    Channel8.Anlg: F2Y2
                    Channel9.Anlg: F2Y3
                    Channel10.Anlg: F2X1
                    Channel11.Anlg: F2X2
                    Channel12.Anlg: F2Z1
                    Channel61.Anlg: Front_Left_AccX
                    Channel62.Anlg: Front_Left_AccY
                    Channel63.Anlg: Front_Left_AccZ
                    Channel64.Anlg: Back_Left_AccX
                    Channel65.Anlg: Back_Left_AccY
                    Channel66.Anlg: Back_Left_AccZ
                    Channel67.Anlg: Front_Right_AccX
                    Channel68.Anlg: Front_Right_AccY
                    Channel69.Anlg: Front_Right_AccZ
                    Channel70.Anlg: Back_Right_AccX
                    Channel71.Anlg: Back_Right_AccY
                    Channel72.Anlg: Back_Right_AccZ
            events:
                    A: Force Plate Zeroing
                    B: Calibration Pose
                    C: First Normal Walking
                    D: Longitudinal Perturbation
                    E: Second Normal Walking
                    F: Unloaded End
            files:
                    mocap: mocap-058.txt
                    record: record-058.txt
                    meta: meta-058.yml
  \end{verbatim}
  \caption{An example meta data YAML file.}
  \label{fig:example-meta-data}
\end{figure}

\begin{description}
  \item[analog-channel-map] A key value mapping of strings specifying the name
    of the signal emmitted from the analog channels of the NI USB XXX.
  \item[cortex-version] (string) Matches the version of Cortex used to record
    the trial.
  \item[datetime] (string) A date formatted string giving the date and/or time
    of the trial in the \verb|YYYY-MM-DD| format.
  \item[dflow-version] (string) Matches the version of D-Flow used to record
    the trial.
  \item[events] A key value map which prescribes names to the events recorded
    in the record file.
  \item[files] (list) A key value mapping of files associated with this trial
    where the key is the file type and the values are the path to the file
    relative to this meta file.
  \item[hardware-settings] There are tons of settings for the hardware in both
    D-Flow, Cortex, and the other software in the system. This contains any
    non-default settings.
    \begin{description}
      \item[high-performance] (boolean) Indicates whether the D-Flow high
        performance setting was on (True) or off (False).
    \end{description}
  \item[id] (integer) A unique three digit identifier for the trial. All of the
    file names and directories associated with this trial include this.
  \item[marker-map] A string key value map which contains names for the
    markers.
  \item[marker-set] (string) Indicates the HBM \cite{Bogert2013} marker
    set used during the trial, either full, lower, or NA.
  \item[nominal-speed] (float) The nominal or base speed during the trial.
  \item[nominal-speed-units] (string) The units of the nominal speed.
  \item[notes] {string} Notes about the trial.
  \item[pitch] (boolean) Indicates if the pitch degree of freedom was acutated
    during the trial.
  \item[stationary-platform] (boolean) Indicates whether the treadmill
      sway or pitch motion was actuated during the trial. If this flag is
      false, the measured ground reaction forces must be compensated for the
      inertial affects and be expressed the forces and moments in the motion
      capture reference frame.
  \item[subject-id] (integer) A number corresponding to the subject in the
    trial.
  \item[sway] (boolean) Indicates if the lateral (sway) degree of freedom was
    acutated during the trial.
\end{description}

@@

\begin{table}
  \centering
  \caption{Descriptions of the 47 markers used in this study.}
  \begin{tabular}{rlll}
    1  & LHEAD & Left head                             & Just above the ear, in the middle. \\
    2  & THEAD & Top head                              & On top of the head, in line with the LHEAD and RHEAD. \\
    3  & RHEAD & Right head                            & Just above the ear, in the middle. \\
    4  & FHEAD & Forehead                              & Between line LHEAD/RHEAD and THEAD a bit right from center. \\
    5  & C7    & C7                                    & On the 7th cervical vertebrae. \\
    6  & T10   & T10                                   & On the 10th thoracic vertbrae. \\
    7  & SACR  & Sacrum bone                           & on the scacral bone. \\
    8  & NAVE  & Navel                                 & On the navel. \\
    9  & XYPH  & Xiphoid process                       & Xiphoid process of the sternum. \\
    10 & STRN  & Sternum                               & On the jugular notch of the sternum. \\
    11 & BBAC  & Scapula                               & On the inferior angle fo the right scapular. \\
    12 & LSHO  & Left shoulder                         & Left acromion. \\
    13 & LDELT & Left deltoid muscle                   & Apex of the deltoid muscle. \\
    14 & LLEE  & Left lateral elbow                    & Left lateral epicondyle of the elbow. Upper one in the T-Pose. \\
    15 & LMEE  & Left medial elbow                     & Left medial epicondyle of the elbow. Lower on in the T-Pose. \\
    16 & LFRM  & Left forearm                          & On 2/3 on the line between the LLEE and LMW. \\
    17 & LMW   & Left medial wrist                     & On styloid process radius, thumb side. \\
    18 & LLW   & Left lateral wrist                    & On styloid process ulna, pinky side. \\
    19 & LFIN  & Left fingers                          & Center of the hand. Caput metatarsal 3. \\
    20 & RSHO  & Right shoulder                        & Right acromion. \\
    21 & RDELT & Right deltoid muscle                  & Apex of deltoid muscle. \\
    22 & RLEE  & Right lateral elbow                   & Right lateral epicondyle of the elbow. Lower one in the T-pose. \\
    23 & RMEE  & Right medial elbow                    & Right medial epicondyle of the elbow. Lower one in the T-pose. \\
    24 & RFRM  & Right forearm                         & On 1/3 on the line between the RLEE and RMW. \\
    25 & RMW   & Right medial wrist                    & On styloid process radius, thumb side. \\
    26 & RLW   & Right lateral wrist                   & On styloid process ulna, pinky side. \\
    27 & RFIN  & Right fingers                         & Center of the hand. Caput metatarsal 3. \\
    28 & LASIS & Pelvic bone left front                & Left anterior superior iliac spine. \\
    29 & RASIS & Pelvic bone right front               & Right anterior superior iliac spine. \\
    30 & LPSIS & Pelvic bone left back                 & Left posterior superio iliac spine. \\
    31 & RPSIS & Pelvic bone right back                & Right posterior superior iliac spine. \\
    32 & LGTRO & Left greater trochanter of the femur  & On the cetner of the left greater trochanter. \\
    33 & FLTHI & Left thigh                            & On 1/3 on the line between the LFTRO and LLEK. \\
    34 & LLEK  & Left lateral epicondyle of the knee   & On the lateral side of the joint axis. \\
    35 & LATI  & Left anterior of the tibia            & On 2/3 on the line between the LLEK and LLM. \\
    36 & LLM   & Left lateral malleoulus of the ankle  & The center of the heel at the same height as the toe. \\
    37 & LHEE  & Left heel                             & Center of the heel at the same height as the toe. \\
    38 & LTOE  & Left toe                              & Tip of big toe. \\
    39 & LMT5  & Left 5th metatarsal                   & Caput of the 5th metatarsal bone, on joint line midfoot/toes. \\
    40 & RGTRO & Right greater trochanter of the femur & On the cetner of the right greater trochanter. \\
    41 & FRTHI & Right thigh                           & On 2/3 on the line between the RFTRO and RLEK. \\
    42 & RLEK  & Right lateral epicondyle of the knee  & On the lateral side of the joint axis. \\
    43 & RATI  & Right anterior of the tibia           & On 1/3 on the line between the RLEK and RLM. \\
    44 & RLM   & Right lateral malleoulus of the ankle & The center of the heel at the same height as the toe. \\
    45 & RHEE  & Right heel                            & Center of the heel at the same height as the toe. \\
    46 & RTOE  & Right toe                             & Tip of big toe. \\
    47 & RMT5  & Right 5th metatarsal                  & Caput of the 5th metatarsal bone, on joint line midfoot/toes. \\
  \end{tabular}
  \label{tab:marker-labels}
\end{table}
